Peridynamic Plates and Flat Shells: A non-ordinary, state-based model

### 2014-08-01 response/response.tex

  \item The Appendix on Frechet derivatives is not required; you can simply refer to [1].
  {\color{red}
     \begin{itemize}
         \item While a reference to [1] provides readers with all the necessary tools to verify our derivations, those unfamiliar with Fr\'echet derivatives will find it far easier to follow the appendix.  Because readers are not yet accustomed to this sort of evaluation, especially for trigonometric and compound vector states, we feel that retaining the appendix is a solid compromise between keeping the body of the paper readable and allowing interested readers to quickly verify or imitate our derivations. Unless the reviewer insists upon it's removal, we prefer to keep it.

@@

  {\color{red}
     \begin{itemize}
        \item Shell models resist in-plane or membrane deformations, as opposed to plates, which resist only transverse deformations. This is noted on page 10:
        \quote{To create a plate model that also resists these deformations, i.e. a flat shell, we combine the bond-pair model with a two-dimensional version of the original bond-based linearly-elastic peridynamic solid model from [10].  We use the adjective ``flat'' to indicate that, at least with consideration to the discretization chosen in this paper, a more complex discretization scheme will have to be utilized to accurately model ``curved shells''}

@@

\section{Reviewer}
\subsection*{General Statement}
The manuscript is a well-written account of developing a model of plates/shells within the peridynamic mechanic theory.

I have several minor comments and one final comment that is not so minor but can be addressed.
%
\subsection*{Specific Comments}

\begin{enumerate}

  \item The authors several times use the phrase "ill-defined". Probably more apt is "undefined". Jump discontinuities are undefined witinh the classical elastic theory.
%
     {\color{red}
     \begin{itemize}
        \item Changed in all locations
     \end{itemize}}
%
  \item Page 4 uses the phrase "to eliminate" when "mitigate" is more appropriate.
%
     {\color{red}
     \begin{itemize}
        \item Changed
     \end{itemize}}
%
  \item Pg 5. I don't think we "must" use the concept of peridynamic states. This is  choice. The paper http://dx.doi.org/10.1007/s10659-012-9418-x discusses an alternative formulation of the peridynamic equations for linear elasticity, and is able to precisely describe the class of deformations. And so there is a deeper concept lurking that "must" be modeled.
%
     {\color{red}
     \begin{itemize}
        \item Eliminated word ``must''
     \end{itemize}}
%
  \item The authors write "This convergence only continues to a minimum horizon, below which the discretized equation of motion (eq. (9)) ceases to accurately approximate the continuous integral formulation (eqs. (1) and (3)). The minimum horizon size depends on the discretization; it appears that twice the node spacing is insufficient, and that three times the node spacing is insufficient." These two sentences suggest that something is awry with the discretization. It seems as if the simple replacement of integrals with sums  is simply to simple to be viable since the horizon depends upon the particle density. Shouldn't these two parameters be separated? Can the authors hold the horizon fixed and let the particle density increase? Except for the potential cost, this would settle the question. Maybe it's a good idea to point out that better numerical methods are needed? Again, the paper http://dx.doi.org/10.1007/s10659-012-9418-x describes a variational formulation; wouldn't this form a basis for a conforming FEM?
%
     {\color{red}
     \begin{itemize}
        \item Replaced figure 6 to show the effect of changing particle density with fixed horizon size. With more cases plotted, it is clearer that results are independent of particle density above a minimum threshold.
        \item Edited referring sentence to explain the updated plot:
        \begin{quotation}
        The difference is evident in fig. 6, which also shows that results are insensitive to fineness of discretization once the minimum horizon criterion is met.
        \end{quotation}
    \item The focus of this paper is the physical model rather than the numerical methods; however, it is true that a conforming FEM would alleviate issues of convergence, linear patch test consistency, etc. it would also introduce the added difficulty of adaptively integrating to resolve discontinuities which is the primary attractiveness of the discretization we present as well as the theory of peridynamics in general.
     \end{itemize}}
%
\end{enumerate}

### 2014-08-01 response/response.tex

  \item The Appendix on Frechet derivatives is not required; you can simply refer to [1].
  {\color{red}
     \begin{itemize}
         \item While a reference to [1] provides readers with all the necessary tools to verify our derivations, those unfamiliar with Fr\'echet derivatives will find it far easier to follow the appendix.  Because readers are not yet accustomed to this sort of evaluation, especially for trigonometric and compound vector states, we feel that retaining the appendix is a solid compromise between keeping the body of the paper readable and allowing interested readers to quickly verify or imitate our derivations. Unless the reviewer insists upon its removal, we prefer to keep it.

@@

  {\color{red}
     \begin{itemize}
        \item Shell models resist in-plane or membrane deformations, as opposed to plates, which resist only transverse deformations. This is noted on page 10:
        \begin{quotation}To create a plate model that also resists these deformations, i.e. a flat shell, we combine the bond-pair model with a two-dimensional version of the original bond-based linearly-elastic peridynamic solid model from [10].
        \end{quotation}
          We use the adjective ``flat'' to indicate that, at least with consideration to the discretization chosen in this paper, a more complex discretization scheme will have to be utilized to accurately model ``curved shells''

### 2014-09-03 response/response_2.tex

\documentclass{article}
\usepackage[left=1.0in,right=1.0in,top=1.0in,bottom=1.0in]{geometry}
\usepackage{fancyhdr}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
%\usepackage[normalem]{ulem}
\usepackage{cancel}
\definecolor{light-gray}{gray}{0.5}

\begin{document}

\begin{center}
    {\LARGE \bf Point-by-Point Response to Reviewer's Comments} \\
     Author's Responses in {\color{red} Red}
\end{center}

%%%% First Reviewer %%%%
\section*{Reviewer Comments}
%

\begin{enumerate}
%
   \item I am not totally convinced by the authors arguments that the novelty of this paper is sufficiently high as to merit publication in IJSS. There are certainly differences from the approach used in [6], but I that these differences are largely algebraic and not conceptual. Certainly, it will require much tedious algebra to use the asymptotic expansion approach from [6] in a state-based setting. This method on the other hand has a critical difficulty that I pointed out in the first review but was not at all addressed in the response.

   {\color{red}
	It’s possible that we were not clear enough in the manuscript, but the differences between this paper and [6] are nearly entirely conceptual, stemming from a completely different way of characterizing bending. In this paper, bending is a fundamental deformation mode, i.e. there are forces that resist angle change, rather than the result of extension deformation that varies through the thickness, i.e. forces that resist only extension, but vary through the thickness. While it may not be the easiest way to represent thin plate bending, it opens the door for continuum analysis of materials that resist bending in different ways. For example, a graphene sheet only one atom thick resists bending without any thickness for displacement to vary along, and a lipid bilayer (sans inclusions) resists isotropic bending but does not resist deviatoric bending at all. Before moving on to these more exotic materials, it is necessary to first build up the simplest models, even if they don’t initially outperform the state of the art for the simplest problems. We started with the simplest possible bending model - the Euler beam in our previous paper [15], and this paper extends that work to the simplest 2D model - a Kirchhoff plate. The goal is that this model will serve as a foundation for models that hopefully outperform the state of the art in their ability to simulate bending behavior for new, complex materials, e.g. meta-materials.
	}
  \item In this paper, one has to compare with standard continuum models and do energy matching. Suppose one were in a situation where one is unsure of the correct continuum model (e.g. thick shells). Then what do we compare it with? The approach in [6] has no such issues.”

   {\color{red}
     The ability to model thick shells is an advantage of [6] over our work, just as the ability to model arbitrary Poisson’s ratios is an advantage of our work over [6]. That said, it just pushes the energy matching back one step, because the bond-based peridynamic solid model is produced by energy matching with a classical solid material. Please see Silling and Askari (2004), Equation 22, where the constitutive model used in [6] is clearly arrived at by energy matching. Other departures from Kirchhoff plate theory, such as nonlinear material behavior, are harder to incorporate with the thickness integral. For example, the damage model in [6] is a function of bottom-plane extension. If only the extension of the bottom surface is compared to a critical stretch, then downward curvature will never result in damage - the plate could be rolled into a cylinder without failing in one direction, and the same deformation in the opposite direction would produce failure. This is likely acceptable in a model that is used to handle bending components of a deformation that is primarily in-plane, but would have to be modified in a scenario where failure is expected to occur due to excessive bending. Moving the plane to the center or top only changes the type of bending that results in no extension of the tracked plane. This would also be a concern for damage that does not completely penetrate the plate. The model presented in this paper offers a way to handle failure in these scenarios.}
%
%
\end{enumerate}
%

\end{document}
